Paper_analyses

### 2022-02-10 Paper_Analyses_subj_obje_arousal.Rmd
last push of simulations for the day

```{r}
View(resampled_temptest)
colnames(resamp_1st)
colnames(resampled_temp_test)
 # create emopty dataframe
resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 13))
# cnames_resamp<- names(resampled_temp)
# colnames(resamp_1st)<- names(resampled_temp)
colnames(resamp_1st)<- cnames_resamp
colnames(resamp_1st)
# create emoty  storage rame for eigenvakues
eigen_first<- as.data.frame(eugentest)
eigen_first[,]<- NA

@@

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))
  resampled_temp<- fabricatr::resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
                                  N = c(51,51),
                                  ID_labels = c("ssid", "stimDescription"),
                                  unique_labels = TRUE)
  resampled_temp$sim_no = i
  resampled_temp$ssid_new <- as.factor(substr(resampled_temp$stimDescription_unique,1,6))
  resampled_temp$newstim <- substr(resampled_temp$stimDescription_unique,7,30)
  # resampled_temp$stimDescription<- as.factor(resampled_temp$stimDescription)

@@

clustering_new_pre_PCA3.1.scale_agg_bystim<- clustering_new_pre_PCA3.1%>%
  group_by(stimDescription)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg<- clustering_new_pre_PCA3.1.scale_agg_bystim%>%
  mutate_if(is.numeric, scale)

@@

# this is slow so need to figure  a better way to to this but for now
clustering_new_pre_PCA3.1_copy %>%
  subset(ssid == 304 &val_cut_iaps == "mid" & aro_cut_iaps == "low" )%>%
  group_by(ssid)%>%
  transform(pup_basCor = sample(pup_basCor, replace = F),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

@@

resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
  group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = F),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

@@

# agg by pp

@@

# run PCA on the resampled data
  # colnames(resampled_temp_bysubj)
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

@@

```
Agg within participant by neg pos etc (using normative data)
With and without selfreports

```{r}
?cut
#create valence categories based ion self reports (IAPS validation)
clustering_new_pre_PCA3_val_vat<- clustering_new_pre_PCA3%>%
  mutate(valence_iaps_cat = cut(ValenceMean,3, labels = c("neg", "mid", "pos")))

>>>>

```{r}
View(resampled_temptest)
colnames(resamp_1st)
colnames(resampled_temp_test)

 # create emopty dataframe
resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 13))
# cnames_resamp<- names(resampled_temp)
# colnames(resamp_1st)<- names(resampled_temp)
colnames(resamp_1st)<- cnames_resamp
colnames(resamp_1st)
# create emoty  storage rame for eigenvakues
eigen_first<- as.data.frame(eugentest)
eigen_first[,]<- NA

@@

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
for (i in 1:5000) {
  message(sprintf("$$$$$RUNING sim %i", i))
  resampled_temp<- fabricatr::resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
                                  N = c(51,51),
                                  ID_labels = c("ssid", "stimDescription"),
                                  unique_labels = TRUE)
  resampled_temp$sim_no = i
  resampled_temp$ssid_new <- as.factor(substr(resampled_temp$stimDescription_unique,1,6))
  resampled_temp$newstim <- substr(resampled_temp$stimDescription_unique,7,30)
  # resampled_temp$stimDescription<- as.factor(resampled_temp$stimDescription)

@@

clustering_new_pre_PCA3.1.scale_agg_bystim<- clustering_new_pre_PCA3.1%>%
  group_by(stimDescription,val_cut_iaps)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg<- clustering_new_pre_PCA3.1.scale_agg_bystim%>%
  ungroup()%>%
  mutate_if(is.numeric, scale)

clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$val_cut_iaps

@@

# this is slow so need to figure  a better way to to this but for now
clustering_new_pre_PCA3.1_copy %>%
  subset(ssid == 304 &val_cut_iaps == "mid" & aro_cut_iaps == "low" )%>%
  group_by(ssid)%>%
  transform(pup_basCor = sample(pup_basCor, replace = TRUE),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

@@

for (i in 1:10000) {
  message(sprintf("$$$$$RUNING sim %i", i))

# changed below to replace treue - shuflle with replacement
  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
resampled_temp_reshuf <-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
  group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = TRUE),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
            arousal = sample(arousal, replace = TRUE),
            valence = sample(valence, replace = TRUE))

@@

visualise resshufled null data

eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(bins = 500, alpha = .2)+
    geom_density(alpha = .3)+
  # facet_grid(~component)+
    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(aes(xintercept = perc_5, linetype = "dashed"))+
  geom_vline(aes(xintercept = perc_95, linetype = "dashed"))+
  ggtitle("distribution of boostraped eigen values for component  1 
          red dot = observed eigenvalue, boostrapped 95%CI")+
  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")+
  ylim(0,10)

t.testsample1_reshudle<- eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )

t.testsample1_reshudle$eigen_extreme <- t.testsample1_reshudle$eigenvalue>= res.mfa_bio_vs_self2_k2$eig[1]
table(t.testsample1_reshudle$eigen_extreme)

?binom.test
binom.test(c(0,1000))

# let's do component 2

t.testsample1_reshudledim2<- eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 2" )

t.testsample1_reshudledim2$eigen_extreme <- t.testsample1_reshudledim2$eigenvalue>= res.mfa_bio_vs_self2_k2$eig[2]
table(t.testsample1_reshudle$eigen_extreme)

eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(bins = 500, alpha = .2)+
    geom_density(alpha = .3)+
  # facet_grid(~component)+
    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(aes(xintercept = perc_5, linetype = "dashed"))+
  geom_vline(aes(xintercept = perc_95, linetype = "dashed"))
  # ggtitle("distribution of boostraped eigen values for component  1 
  #         red dot = observed eigenvalue, boostrapped 95%CI")+
  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
  # ylim(0,10)

```
cor reshudl

```{r}
cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "valenc")%>%
  mutate(valenc_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[5,1]),
         valenc_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[5,2]))%>%
  mutate(prob_extree_vl_d1 = (sum(valenc_cor_extreme_d1)/n()),
         prob_extree_val_d2 = (sum(valenc_cor_extreme_d2)/n()))
# p 0.019	0.532

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "arousa")%>%
  mutate(arous_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[4,1]),
         arous_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[4,2]))%>%
  mutate(prob_extree_vl_d1 = (sum(arous_cor_extreme_d1)/n()),
         prob_extree_val_d2 = (sum(arous_cor_extreme_d2)/n()))
#  p 0.532; 0.019

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "pup_ba")%>%
  mutate(pup_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[1,1]),
         pup_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[1,2]))%>%
  mutate(prob_extree_puup_d1 = (sum(pup_cor_extreme_d1))/n(),
         prob_extree_puup_d2 = (sum(pup_cor_extreme_d2))/n())

```
# not significant

# scr

```{r}
cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "Bio_Me")%>%
  mutate(hr_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[2,1]),
         hr_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[2,2]))%>%
  mutate(prob_extree_hr_d1 = (sum(hr_cor_extreme_d1))/n(),
         prob_extree_hr_d2 = (sum(hr_cor_extreme_d2))/n())
# p< .016 d1 p> ,05 d2

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "log_BI")%>%
  mutate(scr_cor_extreme_Dim.1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[3,1]),
         scr_cor_extreme_Dim.2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[3,2]))%>%
  mutate(prob_extree_scr_dim1 = (sum(scr_cor_extreme_Dim.1))/n(),
         prob_extree_scr_dim2 = (sum(scr_cor_extreme_Dim.2))/n())

# cor nor significant in any dimension p > p05

partials_first_reshuf%>%
  mutate(dimension = as.factor(substr(rownames(partials_first_reshuf), 1,4)),
         group = as.factor(substr(rownames(partials_first_reshuf), 5,9)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(dimension, group)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(bins = 500)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

partials_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(partials_first_reshuf), 1,8))) %>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%

  subset(variable == "log_BI")%>%
  mutate(scr_cor_extreme_Dim.1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[3,1]),
         scr_cor_extreme_Dim.2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[3,2]))%>%
  mutate(prob_extree_scr_dim1 = (sum(scr_cor_extreme_Dim.1))/n(),
         prob_extree_scr_dim2 = (sum(scr_cor_extreme_Dim.2))/n())

groups_first_reshuf<- groups_first_reshuf%>%
  mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4)))

group_cordf<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)
group_cordf$group<-as.factor(substr(rownames(group_cordf), 1,4))

groups_first_reshuf<- left_join(groups_first_reshuf, group_cordf, by = "group")

# groups_first_reshuf%>%
#   mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4))) %>%
#     subset(!is.na(Dim.1)) %>%
#   # create interval per variable

View(groups_first_reshuf)
groups_first_reshuf%>%
  gather(dimension, value_dimenion, -group, -sim_no, -Dim.1.y, -Dim.2.y) %>%
  # -perc_5,-perc_95, 
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%

  ggplot(aes(value_dimenion)) +
  geom_histogram(bins = 500)+
  geom_vline(aes(xintercept = Dim.1.y), linetype = "dashed", color = "red")+
   geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
  facet_grid(dimension~group)+

  theme_classic()

res.mfa_bio_vs_self2_k2$group$correlation

```
# agg by pp

@@

# run PCA on the resampled data
  colnames(resampled_temp_bysubj)
    # message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

@@

cor_first_bysubj %>%
  mutate(variable = as.factor(substr(rownames(cor_first_bysubj), 1,6)))%>%
    subset(!is.na(Dim.2)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.2)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

```
much less conistent

```{r}
groups_first_bysubj%>%
  gather(dimension, value_dimenion, -group, -sim_no) %>%
  # -perc_5,-perc_95, 
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%

  ggplot(aes(value_dimenion)) +
  geom_histogram(bins = 500)+
  geom_vline(aes(xintercept = Dim.1.y), linetype = "dashed", color = "red")+
   geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
  facet_grid(dimension~group)+
  theme_classic()

resample agg by sbj

```{r}
colnames(resamp_1st_bysubj_reshuf)
 # create emopty dataframe
resamp_1st_bysubj_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 7))
cnames_resamp_bysubj_reshuf<- names(resampled_temp_bysubj_reshuf)

colnames(resamp_1st_bysubj_reshuf)<- cnames_resamp_bysubj_reshuf
colnames(resamp_1st_bysubj_reshuf)
# create emoty  storage rame for eigenvakues
eigen_first_bysubj_reshuf<- as.data.frame(eugentest)
eigen_first_bysubj_reshuf[,]<- NA

# eigen_first_bysubj_reshuf<- as.data.frame(eigen_first_bysubj_reshuf)

# create empty storage for correlations
cor_first_bysubj_reshuf<- as.data.frame(cortest)
cor_first_bysubj_reshuf[,]<- NA
# cor_first_bysubj_reshuf<- as.data.frame(cor_first_bysubj_reshuf)

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first_bysubj_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first_bysubj_reshuf[,]<- NA
partials_first_bysubj_reshuf
partials_first_bysubj_reshuf$sim_no<- NA

# hierarquical clustering
clustering_new_pre_PCA3.1$ssid <- as.character(clustering_new_pre_PCA3.1$ssid)
clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
# having clusters as factors causes a subscript oput of bound error

groups_first_bysubj_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first_bysubj_reshuf[,]<- NA
groups_first_bysubj_reshuf
groups_first_bysubj_reshuf$sim_no<- NA

for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))
  # changed below to replace treue - shuflle with replacement
  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
resampled_temp_bysubj_reshuf <- clustering_new_pre_PCA3.1.scale_agg_bysid %>%
  # group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = TRUE),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
            arousal = sample(arousal, replace = TRUE),
            valence = sample(valence, replace = TRUE))

  resampled_temp_bysubj_reshuf$sim_no = i

# run PCA on the resampled data
# ?list
  colnames(resampled_temp_bysubj_reshuf)
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_bysubj_reshuf <- FactoMineR::MFA(resampled_temp_bysubj_reshuf[,c(1:6)], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
message(sprintf("$$$$$storing PCA %i", i))
eugentest_bysubj_reshufl<- as.data.frame(mfa.res_bysubj_reshuf$eig[1:2,])
eugentest_bysubj_reshufl$sim_no<- i

cortest_bysubj_reshufl<- as.data.frame(mfa.res_bysubj_reshuf$quanti.var$cor)
cortest_bysubj_reshufl$sim_no = i

partials_temp_bysubj_reshuf<- as.data.frame(mfa.res_bysubj_reshuf$partial.axes$cor)
partials_temp_bysubj_reshuf$sim_no = i

# groups
group_temp_bysubj_reshuf<- as.data.frame(mfa.res_bysubj_reshuf$group$cos2)
group_temp_bysubj_reshuf$sim_no = i

# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st_bysubj_reshuf<- (bind_rows(resamp_1st_bysubj_reshuf, resampled_temp_bysubj_reshuf))
eigen_first_bysubj_reshuf<- bind_rows(eigen_first_bysubj_reshuf, eugentest_bysubj_reshufl)
cor_first_bysubj_reshuf<- bind_rows(cor_first_bysubj_reshuf, cortest_bysubj_reshufl)
partials_first_bysubj_reshuf<- bind_rows(partials_first_bysubj_reshuf, partials_temp_bysubj_reshuf)
groups_first_bysubj_reshuf<- bind_rows(groups_first_bysubj_reshuf, group_temp_bysubj_reshuf)
  message(sprintf("$$$$$completed iteration%i", i))
}

save.image("subjobjPCAfeb9.RData")

visualise resshufled null data

eigen_first_bysubj_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the
  ggplot(aes(eigenvalue))+
  geom_histogram(bins = 500, alpha = .2)+
    geom_density(alpha = .3)+
  # facet_grid(~component)+
    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(xintercept = res.mfa_agg_bysubj$eig[1], linetype = "dashed")

# no significant

# dimension 2
eigen_first_bysubj_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the
  ggplot(aes(eigenvalue))+
  geom_histogram(bins = 500, alpha = .2)+
    geom_density(alpha = .3)+
  # facet_grid(~component)+
    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(xintercept = res.mfa_agg_bysubj$eig[2], linetype = "dashed")
# also not significant

eigen_first_bysubj_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>%
  mutate(extreme_eigen_count = eigenvalue>= res.mfa_agg_bysubj$eig[1])%>%
  mutate(extreme_eigen_count_prob = (sum(extreme_eigen_count))/n())

# p value 0.702 as we can see in the graph

res.mfa_agg_bysubj$quanti.var$cor

cor_first_bysubj_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  group_by(variable)%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   # geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  theme_classic()

cor_first_bysubj_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
  subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "Bio_Me")%>%
  mutate(hr_cor_extreme_d1 = abs(Dim.1)>= abs(mfa.res_bysubj_reshuf$quanti.var$cor[2,1]),
         hr_cor_extreme_d2 = abs(Dim.2)>= abs(mfa.res_bysubj_reshuf$quanti.var$cor[2,2]))%>%
  mutate(prob_extree_hr_d1 = (sum(hr_cor_extreme_d1))/n(),
         prob_extree_hr_d2 = (sum(hr_cor_extreme_d2))/n())

PARTIALS

```{r}
# res.mfa_agg_bysubj$partial.axes$cor
partials_first_bysubj_reshuf %>%
  mutate(dimension = as.factor(substr(rownames(partials_first_bysubj_reshuf), 1,4)),
         group = as.factor(substr(rownames(partials_first_reshuf), 5,9)))%>%
    subset(!is.na(Dim.1)) %>%
  group_by(dimension, group)%>%

  ggplot(aes(Dim.1)) +
  geom_histogram(bins = 500)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

groups
variables and dimension corelations

cor_first_bysubj_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +

  facet_grid(~variable)+
  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

Agg within participant by neg pos etc (using normative data)
With and without selfreports

start with bootsrap to estimate CIS
```{r}

clustering_new_pre_PCA3_val_vat_agg_scale # this is the one I need
colnames(clustering_new_pre_PCA3_val_vat_agg_scale)

res.mfa_agg_bysubj_cat_val<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg_scale, 
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

colnames(resampled_temp_bysubj_cat_val)
resamp_1st_bysubj_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 12))

# cnames_resamp_subj<- names(resampled_temp_bysubj_cat_val)
colnames(resamp_1st_bysubj_cat_val)<- cnames_resamp_subj
colnames(resamp_1st_bysubj_cat_val)
# create emoty  storage rame for eigenvakues
eigen_first_bysubj_cat_val<- as.data.frame(eugentest)
eigen_first_bysubj_cat_val[,]<- NA

# create empty storage for correlations
cor_first_bysubj_cat_val<- as.data.frame(cortest)
cor_first_bysubj_cat_val[,]<- NA
# cor_first<- as.data.frame(cor_first)

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first_bysubj_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first_bysubj_cat_val[,]<- NA
partials_first_bysubj_cat_val
partials_first_bysubj_cat_val$sim_no<- NA

groups_first_bysubj_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first_bysubj_cat_val[,]<- NA
groups_first_bysubj_cat_val
groups_first_bysubj_cat_val$sim_no<- NA

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)
library(fabricatr)

clustering_new_pre_PCA3_val_vat_agg_scale$valence_iaps_cat<- as.character(clustering_new_pre_PCA3_val_vat_agg_scale$valence_iaps_cat)

clustering_new_pre_PCA3_val_vat_agg_scale$ssid<- as.character(clustering_new_pre_PCA3_val_vat_agg_scale$ssid)
nrow(clustering_new_pre_PCA3_val_vat_agg_scale)
